---
title: "Finger Tapping Analysis"
author: "Awais Hafeez"
date: "11/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ez)
library(pracma)
library(dplyr)
library(reshape2)
source('stat_smooth_fun_pval.R')
source('summarySE.R')
#library(plyr)
library(data.table)
library(ggpubr)
library(rstatix)
```

## Function


```{r echo=FALSE,include=FALSE}
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
}
```

```{r echo=FALSE, include=FALSE}
set_peaks_column <- function(x){
  peaks <- findpeaks(x,nups = 3,ndowns = 3)
  peaks_idx <- peaks[,2]
  
  is_peak <- rep(FALSE, length(x))
  
  is_peak[peaks_idx] = TRUE
  return(is_peak)
}
```

```{r echo=FALSE,include=FALSE}
corfun<-function(x, y) {
  corr=(cor.test(x, y,
                 alternative="two.sided", method="pearson"))
}
```

```{r echo=FALSE,include=FALSE}
get_ftapping <- function(df_subset){
i1 <- !is.na(inverse.rle(within.list(rle(df_subset$is_reaching), 
     values[c(1, length(values))][values[c(1, length(values))] == FALSE] <- NA)))
data <- df_subset[i1, , drop = FALSE]
return(data)
}
```

```{r echo=FALSE, include=FALSE}
sig_len <- function(df_subset){
  len <- length(df_subset$speed)
  
  data <- as.data.frame(df_subset) %>% 
    mutate(speed_len = len)
  
  return(data)
}
```

```{r echo=FALSE, include=FALSE}
amplitude_CV <- function(df_subset){
  amp_signal <- df_subset$dist_norm
  amp_signal <- amp_signal - mean(amp_signal)
  
  win_len <- 60
  energy_list <- 0
  
  l <- length(amp_signal)
  ra <- l - win_len
  
  for (i in 0:ra){
    
    temp <- amp_signal[i:win_len+1]
    energy_list[i] <- max(temp,na.rm = TRUE) - min(temp,na.rm = TRUE)
  }
  
  
  data <- as.data.frame(df_subset) %>% 
    mutate(windows_CV = sd(energy_list)/mean(energy_list))
  
  return(data)
}
```

```{r echo=FALSE, include=FALSE}
read_and_filter_media <- function(file){
  
  movement <- read_csv(file) 
  dt <- 1/ 60
  numframes = length(movement$Thumb_Tip_X)
  df <- as.data.frame(movement) %>% 
    mutate_at(vars(Thumb_Tip_X:Index_Finger_Tip_Y), funs(ifelse(. == -999, NA, .))) %>% 
    mutate_at(vars(Thumb_Tip_X:Index_Finger_Tip_Y), na.approx, na.rm = FALSE) %>% # lerp
    mutate(frame = 0:(numframes-1))
  # pad data
  paddata <- 100
  
  data <- tibble(frame = (-paddata):(numframes+paddata-1))
  
  data <- data %>%
    left_join(y = df, by = "frame") %>%
    fill(-frame, .direction = "down") %>% # padded NAs replaced with first/last position
    fill(-frame, .direction = "up")
  
  nyq_f <- 30
  
  bf_low <- butter(4, 5/nyq_f , type="low",plane = 'z')
  
  # filter  
  data <- data %>% 
    mutate_at(vars(-frame), function(x) filtfilt(filt = bf_low, x = x)) %>% 
    dplyr::filter(frame >= 0, frame < numframes) %>% 
    mutate(time = frame * dt) %>% 
    select(-frame)
  
  return(data)
}
```

```{r echo=FALSE, include=FALSE}
delta_t <- 0.01667
```
## Aims and Objectives

  Assessment heavily relies on clinician’s experience and his/her ability to detect mild impairments and progressive decline in motor functions in PD progression. Physician analyze and rate motor performance by observing speed, amplitude, rhythm and amplitude decrement as movements are continued. Hence, considerable inter-rater variability and subjective evaluation may result in inaccurate diagnosis and rough quantification. Therefore, we aim to investigate the potential usage of low-cost, portable motion capture system (BIGKAT; developed in our lab, PACLab) for the objective measurement of bradykinesia against commercially available motion capture system Optotrak (Optotrak, NDI Inc).  
  With the aim to overcome the disadvantage of subjective evaluation and to provide more sensitive continuous measures, several instrumental approaches have been proposed to assess bradykinesia via finger tapping and in this study, we sought to investigate the quantitative measures obtained from  Optotrak & BIGKAT and qualitative measures as rated by the neurologist by looking at the smartphone camera videos. Participants were instructed to repeatedly tap their index finger on the thumb as quickly AND as big as possible, while Optotrak, BIGKAT and smartphone recorded FT movements simultaneously.  
  Firslty, as reproted in the previous literature, optoelectronic motion capture system such as Optotrak can significantly differentiate PD patients from healthy controls by statiscally analysing the objective measures extracted from the distance between the thumb and index finger IREDs, as movements are continued. And we aim to draw similar conclusions from expensive Optotrak system. Secondly, how these quntitative measures are correlated with the subjective evaluation of camera videos rated by two nerurologist according to UPDRS scale. And thirdly, we aim to compare BIGKAT performance against Optotrak by running correlation and regression analysis between the quantiative measures obtained from both devices and therefore exploiting its potential usage in large scale, routine clinical settings.  


## Importing data
Finger tapping movement of 60 hands (including left and right) were obtained from 10 patients with idiopathic Parkinsons's disease and 9 healthy controls using BIGKAT and Optotrak by attaching infra-red markers to the thumb and finger tip. Four trials of 17s length were recorded from each hand.  
  
```{r message=FALSE, warning=FALSE}
ft_files <- tibble(files = list.files("csvfiles_big_op_unfil", full.names= TRUE, recursive = TRUE))

FT_movement <- ft_files %>% 
  mutate(data = map(files, read_csv)) %>% 
  unnest(data, .drop = FALSE) %>% 
  separate(fileName, c("Device","ppid","Hand","trial_num"), sep = "_",extra='drop') %>%
  select(-files) %>%
  mutate(pp = substr(ppid, 1, 2))%>%
  mutate_at(vars(pp), funs(ifelse(pp == " P", "Patient", "Control"))) %>% 
  select(Device,ppid,pp,Hand,trial_num,everything())%>% 
  data.frame()
```

## Processing
3D coordinates of the finger tapping movement obtained from both devices (BIGKAT & Optotrak) were standarised across all trials, by using the maximum opening distance between finger and thumb tip and normalizing this to a value of 1. Calculating absolute speed as a rate of change of the distance between finger and thumb tip over time. Deteriming the movement onset using threshold of 50mm/s.  
  
```{r message=FALSE, warning=FALSE}

FT_analysis <- FT_movement  %>% 
  group_by(ppid,Hand,trial_num,Device) %>% 
  mutate(time = (row_number() * delta_t)-delta_t,
         distance_thumb_finger = ((finger_x - thumb_x)^2 + (finger_y - thumb_y)^2 + (finger_z - 
                                                                                     thumb_z)^2)^0.5,
         abs_dis = abs(distance_thumb_finger)) %>% 
  #select(-starts_with('th'),-starts_with('fi')) %>%
  mutate(dist_norm = normalize(distance_thumb_finger),
         abs_dist_norm = normalize(abs_dis),
         speed = abs(c(NA,diff(distance_thumb_finger)/diff(time))),
         is_reaching = speed > 50)
         #is_tapping = abs_dis >80,
         #acc = abs(c(NA,diff(speed)/diff(time))),
         #is_reaching = acc > 1000)
```

### Trimming Data
Trimming data based on customized 'get_ftapping' function to remove the first set of rows where the absolute speed is lower than threshold.  
  
```{r include=TRUE}
df_ft_trim <- FT_analysis  %>%
  select(ppid, Hand, trial_num, Device, pp, dist_norm,time,abs_dis,is_reaching,speed) %>% 
  group_by(ppid,Hand,trial_num,Device) %>%
  dplyr::filter(!is.na(is_reaching)) %>% 
  do(get_ftapping(.)) %>% 
  mutate(t =(row_number()*delta_t)-delta_t)
```

#### Trial Visulaization
  
  Plotting absolute distance over time obtained from bith devices for a single trial and participant. 

#### Healthy Control 
```{r include=FALSE}
ft_vel1 <- df_ft_trim %>% dplyr::filter(ppid == " C06 ") %>% dplyr::filter(trial_num == " 1") %>% filter( Hand == " Left ")
```

  Figure below shows amplitude variation over time for a healthy control  
    
```{r echo=FALSE}
a <- ggplot(ft_vel1 %>% filter(t <= 12)  ,
       aes(x=t, y = dist_norm, color=Device))+
       geom_path(show.legend = FALSE ,size = 0.8) +
  xlab('') +
  ylab('') +
  theme_bw()+
  theme(axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        legend.box.just = "left",legend.justification = c(0.9999,0.9999),
        legend.position=c(0.9999,0.9999),legend.title = element_blank(),
        legend.background = element_rect(fill = alpha("white",0)),
        plot.title = element_text(hjust = 0.5))+
  guides(colour = guide_legend(nrow = 1))+
  labs(title = 'Distance b/w thumb & Finger (mm)')
  ggsave('graphs/C06_Left_T1_op.png',type='cairo', width= 6, height= 4, dpi = 800)
```
#### PD Patient 
```{r include=FALSE}
ft_vel2 <- df_ft_trim %>% filter(ppid == " P70 ") %>% filter(trial_num == " 2") %>% filter( Hand == " Right ")
```

  Figure below shows amplitude variation over time by PD patient
    
```{r echo=FALSE}
b <- ggplot(ft_vel2 %>% filter(t <= 12)  ,
       aes(x=t, y = dist_norm, color=Device))+
       geom_path(size = 0.8) +
  xlab("Time (s)") +
  ylab("") +
  theme_bw()+
  theme(axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        legend.box.just = "top",legend.justification = c(1,1.1),
        legend.position=c(1,1.1),legend.title = element_blank(),
        legend.background = element_rect(fill = alpha("white",0)))+
  guides(colour = guide_legend(nrow = 1))
  ggsave('graphs/P72_Right_T2_op.png',type='cairo', width= 6, height= 4, dpi = 800)
```

```{r}
ggarrange(a, b, labels = c("a", "b"),
                    ncol = 1, nrow = 2)+
ggsave('graphs/P72_C06_op.png',type='cairo', width= 7, height= 4, dpi = 800)
```

### Average speed and average speed peaks
A measure of speed was calculated as the mean rate of change of the normalised distance between finger and thumb tip over time.

```{r echo=FALSE,include=FALSE}
df_speed <-  df_ft_trim %>% dplyr::filter(!grepl("P64",ppid)) %>% 
  select(ppid, Hand, trial_num, Device, pp, dist_norm,t) %>% 
  group_by(ppid,Hand,trial_num,Device,pp) %>% 
  mutate(mean_dis = dist_norm - mean(dist_norm),
         speed = abs(c(NA,diff(mean_dis)/diff(t)))) %>% 
  dplyr::filter(!is.na(speed))

```

```{r include=FALSE}
df_speed_ave <-  df_speed %>% 
  group_by(ppid,Hand,trial_num,Device,pp) %>%
  mutate(ave_speed = mean(speed),
         is_peak = set_peaks_column(mean_dis)) %>% 
  dplyr::filter(is_peak) %>% 
  mutate(speed_peak = abs(c(NA, diff(speed)/diff(t)))) %>%
  dplyr::filter(!is.na(speed_peak)) %>% 
  mutate(ave_speed_peak = mean(speed_peak))
```



```{r include=FALSE}
df_avg_speed_op <- df_speed_ave %>% ungroup() %>% filter(Device == 'OPTOTRAK ') 
```


```{r echo=FALSE}
ave_speed_one.way <- aov(ave_speed ~ pp, data = df_avg_speed_op)
summary(ave_speed_one.way)

```
#### Effect of pp on average speed
```{r }
avSpeed.pp_pwc <- df_avg_speed_op %>%
  pairwise_t_test(
    ave_speed ~ pp, paired = FALSE,
    p.adjust.method = "bonferroni"
    )
avSpeed.pp_pwc
```
#### cohen's d
```{r echo=FALSE}

speed.pp_d <- df_avg_speed_op %>%
  cohens_d(ave_speed ~ pp, paired = FALSE)
speed.pp_d 
```

##### two way 
```{r echo=FALSE}
ave_speed_two.way <- aov(ave_speed ~ pp*Hand, data = df_avg_speed_op)
summary(ave_speed_two.way)

```

#### SE,SD, CI

```{r echo=FALSE, message=FALSE, warning=FALSE}
speed_pp_se <- summarySE(df_avg_speed_op, measurevar="ave_speed", groupvars=c("pp"))
speed_pp_se
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
speed_se_pp <- summarySE(df_avg_speed_op, measurevar="ave_speed", groupvars=c("Hand","pp"))
speed_se_pp
```
#### Tukey-HSD Test
Tukey-HSD test is conducted to find significant differences between patients and control. Data from both devices (Bigkat and optotrak) effectively determined speed differences between patients and control as shown in figure. 
```{r echo=FALSE}
speed_pp <- df_avg_speed_op %>%
  group_by(Hand) %>%
  tukey_hsd(ave_speed ~ pp)
speed_pp
```

```{r warning=FALSE, echo=FALSE}
pd <- position_dodge(0.3)
a_speed <- ggplot(speed_se_pp , aes(x=as.factor(pp), y=ave_speed, color=Hand, group=Hand,linetype=Hand)) + 
  geom_errorbar(aes(ymin=(ave_speed-sd), ymax=(ave_speed+sd),
                    color=Hand), size=1, width=.3, position=pd) +
  geom_line(position=pd) +
  geom_point(position=pd, size=3, shape=21, fill="white") + # 21 is filled circle
  xlab("") +
  ylab("Average speed (mm/s)") +
  scale_colour_hue(name="Hand",    # Legend label, use darker colors
                   breaks=c("Left", "Right"),
                   labels=c("Left", "Right"),
                   l=40) +                    # Use darker colors, lightness=40
  expand_limits(y=0) +                        # Expand y range
  scale_y_continuous(breaks=0:8*1) +     
  theme_bw() +
  theme(strip.background = element_rect(color = 'black',fill = 'NA',size = 1.2)) +
  theme(panel.background = element_rect(color = 'black',fill = 'NA',size = 1.2)) +
  stat_pvalue_manual(speed_pp, label ="p.adj.signif",
                     y.position = c(5.9,6.2),
                     xmin = "group1",xmax  = "group2",tip.length = 0,
                     step.group.by = "Hand",linetype ="Hand",
                     color = "Hand",position = pd)+
  labs(color  = "Hand", linetype = "Hand", group = "Hand") +
  #facet_grid(~Device) +
  theme(legend.box.just = "left",legend.justification = c(0.99,0.1), legend.position=c(0.99,0.1))+
  ggsave('graphs/op_trim_average_speed.png',type='cairo', width= 4, height= 4, dpi = 800)
```


### Amplitude variation 

```{r message=FALSE, warning=FALSE}
ft_files_amp <- tibble(files = list.files("csvfiles_big_op", full.names= TRUE, recursive = TRUE))

FT_movement_amp <- ft_files_amp %>% 
  mutate(data = map(files, read_csv)) %>% 
  unnest(data, .drop = FALSE) %>% 
  separate(fileName, c("Device","ppid","Hand","trial_num"), sep = "_",extra='drop') %>%
  select(-files) %>%
  mutate(pp = substr(ppid, 1, 2))%>%
  mutate_at(vars(pp), funs(ifelse(pp == " P", "Patient", "Control"))) %>% 
  select(Device,ppid,pp,Hand,trial_num,everything())%>% 
  data.frame()
```

```{r message=FALSE, warning=FALSE}

FT_analysis_amp <- FT_movement_amp  %>% 
  group_by(ppid,Hand,trial_num,Device) %>% 
  mutate(time = (row_number() * delta_t)-delta_t,
         distance_thumb_finger = ((finger_x - thumb_x)^2 + (finger_y - thumb_y)^2 + (finger_z - 
                                                                                     thumb_z)^2)^0.5,
         abs_dis = abs(distance_thumb_finger)) %>% 
  #select(-starts_with('th'),-starts_with('fi')) %>%
  mutate(dist_norm = normalize(distance_thumb_finger),
         abs_dist_norm = normalize(abs_dis),
         speed = abs(c(NA,diff(distance_thumb_finger)/diff(time))),
         is_reaching = speed > 50)
         #is_tapping = abs_dis >80,
         #acc = abs(c(NA,diff(speed)/diff(time))),
         #is_reaching = acc > 1000)
```

  
```{r include=TRUE}
df_ft_trim_amp <- FT_analysis_amp  %>%
  select(ppid, Hand, trial_num, Device, pp, dist_norm,time,abs_dis,is_reaching,speed) %>% 
  group_by(ppid,Hand,trial_num,Device) %>%
  dplyr::filter(!is.na(is_reaching)) %>% 
  do(get_ftapping(.)) %>% 
  mutate(t =(row_number()*delta_t)-delta_t)
```


```{r message=FALSE, warning=FALSE, echo=FALSE,include=FALSE}
detach("package:plyr", unload = TRUE)
```
A measure of amplitude variability was calculated by dividing each time series into one-second windows, with maximal overlap, and then calculating the coefficient of variation of the mean difference between the maximum and minimum amplitudes in each window. A special function was developed to determine the variation. 
```{r message=FALSE, warning=FALSE}
df_amplitude <- df_ft_trim  %>% dplyr::filter(!grepl("P64",ppid)) %>% 
  select(ppid, Hand, trial_num, Device, pp, dist_norm,t) %>% 
  group_by(ppid,Hand,trial_num,Device) %>%
  do(amplitude_CV(.))
```

```{r message=FALSE, warning=FALSE}
df_amplitude_amp <- df_ft_trim_amp  %>% dplyr::filter(!grepl("P64",ppid)) %>% 
  select(ppid, Hand, trial_num, Device, pp, dist_norm,t) %>% 
  group_by(ppid,Hand,trial_num,Device) %>%
  do(amplitude_CV(.))
```

```{r message=FALSE, warning=FALSE,echo=FALSE,include=FALSE}

df_amplitude_DV <- df_amplitude %>% 
  group_by(ppid,Hand,trial_num,Device,pp) %>% 
  mutate(mean_dis = dist_norm - mean(dist_norm),
         is_peak = set_peaks_column(mean_dis)) %>%
  dplyr::filter(is_peak) %>% 
  mutate(peak_diff = c(NA,diff(mean_dis)-mean(diff(mean_dis)))) %>% 
  dplyr::filter(!is.na(peak_diff)) %>% 
  mutate(DV = sd(peak_diff))
```


```{r include=FALSE}
df_amp_op <- df_amplitude_amp %>% ungroup() %>% filter(Device == 'OPTOTRAK ')
```

#### Two way ANOVA
```{r echo=FALSE}
hand_CV_two.way <- aov(windows_CV ~ Hand, data = df_amp_op%>% filter(pp == 'Patient'))
summary(hand_CV_two.way)
```
```{r}
tukey.amp_hand_pat <- TukeyHSD(hand_CV_two.way)
tukey.amp_hand_pat
```

#### Two way ANOVA
```{r echo=FALSE}
CV_two.way <- aov(windows_CV ~ pp*Hand, data = df_amp_op)
summary(CV_two.way)
```

#### Effect of pp on amplitude decrement
```{r }
CV.pp_pwc <- df_amp_op %>%
  pairwise_t_test(
    windows_CV ~ pp, paired = FALSE,
    p.adjust.method = "bonferroni"
    )
CV.pp_pwc
```
```{r }

CV.pp_d <- df_amp_op %>%
  cohens_d(windows_CV ~ pp,
           paired=FALSE)
CV.pp_d 
```


#### Tukey HSD

```{r}
tukey.amp_two.way <- TukeyHSD(CV_two.way)
tukey.amp_two.way
```


#### SD, SE and CI
```{r echo=FALSE, message=FALSE, warning=FALSE}
amplitude_se_pp <- summarySE(df_amp_op, measurevar="windows_CV", groupvars=c("Hand","pp"))
amplitude_se_pp
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
amp_se_pp <- summarySE(df_amp_op, measurevar="windows_CV", groupvars=c("pp"))
amp_se_pp
```

#### Tukey-HSD Test
```{r echo=FALSE}
amplitude_pp <- df_amp_op %>%
  group_by(Hand) %>%
  tukey_hsd(windows_CV ~ pp)
amplitude_pp
```

```{r message=FALSE, warning=FALSE,echo=FALSE}
pd <- position_dodge(0.3)
b_amp <- ggplot(amplitude_se_pp , aes(x=as.factor(pp), y=windows_CV, colour=Hand, group=Hand,linetype=Hand)) + 
  geom_errorbar(aes(ymin=(windows_CV-sd), ymax=(windows_CV+sd),
                    colour=Hand), size=1, width=.3, position=pd) +
  geom_line(position=pd) +
  geom_point(position=pd, size=3, shape=21, fill="white") + # 21 is filled circle
  xlab("") +
  ylab("Amplitude CoV") +
  scale_colour_hue(name="Hand",    # Legend label, use darker colors
                   breaks=c("Left", "Right"),
                   labels=c("Left", "Right"),
                   l=40) +                    # Use darker colors, lightness=40
  expand_limits(y=0) +                        # Expand y range
  scale_y_continuous(breaks=0:4*0.1) +     
  theme_bw() +
  theme(strip.background = element_rect(color = 'black',fill = 'NA',size = 1.2)) +
  theme(panel.background = element_rect(color = 'black',fill = 'NA',size = 1.2)) +
  stat_pvalue_manual(amplitude_pp, label ="p.adj.signif",
                     y.position = c(0.37,0.4),
                     xmin = "group1",xmax  = "group2",tip.length = 0,
                     step.group.by = "Hand",linetype ="Hand",
                     color = "Hand",position = pd)+
  labs(color  = "Hand", linetype = "Hand", group = "Hand") +

  theme(legend.box.just = "left",legend.justification = c(0.98,0.01), legend.position=c(0.98,0.01),legend.spacing.y = unit(0.01,'cm'))+
  ggsave('graphs/op_trim_Amplitude_variation.png',type='cairo', width= 4, height= 4, dpi = 800)
```



### FFT- Frequency Freatures
A measure of rhythm regularity was calculated by undertaking Fast Fourier Transform to find the distribution of frequencies within each finger tap time series, and then measuring the power of the dominant frequency peak added to the power of the frequencies 0.2 Hz either side of it. A more regular tapping rhythm concentrates power in a narrow frequency band, increasing the power of the dominant frequency peak (and its immediate neighbours), whereas a more irregular tapping rhythm leads to a more widely spread distribution of frequency bands, reducing the power of the dominant frequency peak (and its immediate neighbours).
```{r message=FALSE, warning=FALSE,include=FALSE}
detach("package:plyr", unload = TRUE)
```

```{r message=FALSE, warning=FALSE}
df_fft <-  df_ft_trim %>% dplyr::filter(!grepl("P64",ppid)) %>% 
  select(ppid, Hand, trial_num, Device, pp, dist_norm,time) %>% 
  group_by(ppid,Hand,trial_num,Device,pp) %>% 
  mutate(mean_dis = dist_norm - mean(dist_norm),
         xlen = length(dist_norm),
         NFFT = 2 ^ nextpow2(xlen),
         yf = fft(mean_dis,NFFT)/xlen*2,
         yf = abs(yf),
         Fs = 60,
         step = NFFT/2+1,
         features = TRUE) %>% 
  mutate(features = if_else(row_number() <= step, features, !features)) %>% 
  dplyr::filter(features) %>% 
  mutate(f = Fs / 2 * seq(from=0, to=1, length.out= step)) %>% 
  select(-features,-step,-Fs) %>% 
  mutate(idx = which.max(yf),
         interval = 2,
         idx_int = idx + interval,
         int_idx = idx - interval,
         Freq_feature = ifelse(idx <= interval, sum(yf[1:idx_int]), sum(yf[int_idx:idx_int])),
         t = (row_number()*delta_t)-delta_t) %>% 
  select(-idx,-interval,-idx_int,-int_idx,-xlen)
```


#### Healthy Control 
```{r include=FALSE}
fft_sig <- df_fft %>% dplyr::filter(ppid == " C06 ") %>% dplyr::filter(trial_num == " 1") %>% filter( Hand == " Left ") %>%  filter (Device == "OPTOTRAK ") %>%
  mutate(max_yf = f[which.max(yf)])
```

```{r echo=FALSE}
a_fft <- ggplot(fft_sig , aes(x=f, y = yf, color=Device))+
  geom_path(show.legend = FALSE, size = 0.8) +
  geom_vline(xintercept = fft_sig$max_yf, linetype="dotted", 
                color = "blue", size=1)+
  xlab("") +
  ylab("") +
  labs(title = 'Frequency Distirbution')+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5))
  
  ggsave('graphs/C06_Left_T1_op_fft.png',type='cairo', width= 10, height= 6, dpi = 800)
```

#### PD Patient 
```{r include=FALSE}
fft_sig_pd <- df_fft %>% dplyr::filter(ppid == " P70 ") %>% dplyr::filter(trial_num == " 2") %>% filter( Hand == " Right ") %>% filter (Device == "OPTOTRAK ") %>% 
  mutate(max_yf = f[which.max(yf)])
```

```{r echo=FALSE}
b_fft <- ggplot(fft_sig_pd  ,
       aes(x=f, y = yf, color=Device))+
  geom_path(size = 0.8) +
  geom_vline(xintercept = fft_sig_pd$max_yf, linetype="dotted", 
                color = "blue", size=1)+
  xlab("Frequency (Hz)") +
  ylab("") +
  theme_bw()+
  theme(axis.title.x = element_text(size=12),
        legend.box.just = "top",legend.justification = c(1,0.99),
        legend.position=c(1,0.99),legend.title = element_blank(),
        legend.background = element_rect(fill = alpha("white",0)))+
  ggsave('graphs/P70_Right_T2_op_fft.png',type='cairo', width= 10, height= 6, dpi = 800)
```

```{r}
ggarrange(a_fft, b_fft, labels = c("a", "b"),
                    ncol = 1, nrow = 2)+
ggsave('graphs/P72_C06_op_fft.png',type='cairo', width= 7, height= 4, dpi = 800)
```




```{r include=FALSE}
df_fft_op <- df_fft %>% ungroup() %>% filter(Device == 'OPTOTRAK ')
```

#### one way ANOVA
```{r echo=FALSE}
fft_one.way <- aov(Freq_feature ~ pp, data = df_fft_op)
summary(fft_one.way)
```
#### Effect of pp on Rhythm regularity 
```{r }
fft.pp_pwc <- df_fft_op %>%
  pairwise_t_test(
    Freq_feature ~ pp, paired = FALSE,
    p.adjust.method = "bonferroni"
    )
fft.pp_pwc
```

```{r }

CV.pp_d <- df_amp_op %>%
  cohens_d(windows_CV ~ pp,
           paired=FALSE)
CV.pp_d 
```

#### Two way ANOVA
```{r echo=FALSE}
fft_two.way <- aov(Freq_feature ~ pp*Hand, data = df_fft_op)
summary(fft_two.way)
```
```{r}
tukey.fft_two.way <- TukeyHSD(fft_two.way)
tukey.fft_two.way
```

#### SD, SE & CI
```{r echo=FALSE, message=FALSE, warning=FALSE}
freq_se <- summarySE(df_fft_op, measurevar="Freq_feature", groupvars=c("Hand","pp"))
freq_se
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
freq_se_pp <- summarySE(df_fft_op, measurevar="Freq_feature", groupvars=c("pp"))
freq_se_pp
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
freq_se_hand <- summarySE(df_fft_op, measurevar="Freq_feature", groupvars=c("Hand"))
freq_se_hand
```

```{r}
res.ezaov <- ezANOVA(df_fft_op ,
dv = Freq_feature, # specify dependent variable
wid = ppid, # specify the subject variable
within = .(Hand),
type = 3,detailed = TRUE, return_aov = TRUE)
#res.ezaov
get_anova_table(res.ezaov$ANOVA)
```

##### Tukey-HSD Test
```{r echo=FALSE}
freq_pp <- df_fft_op %>%
  group_by(Hand) %>%
  tukey_hsd(Freq_feature ~ pp)
freq_pp
```
#### Cohen's d
```{r echo=FALSE}
fft.d <- df_fft_op %>% group_by(Hand) %>% 
  cohens_d(Freq_feature ~ pp,
           paired=FALSE)
 fft.d 
```

```{r message=FALSE, warning=FALSE,echo=FALSE}
c_fft <- ggplot(freq_se , aes(x=as.factor(pp), y=Freq_feature, colour=Hand, group=Hand,linetype=Hand)) + 
  geom_errorbar(aes(ymin=(Freq_feature-sd), ymax=(Freq_feature+sd),
                    colour=Hand), size=1, width=.3, position=pd) +
  geom_line(position=pd) +
  geom_point(position=pd, size=3, shape=21, fill="white") + # 21 is filled circle
  xlab("") +
  ylab("Rhythm (mm/Hz)") +
  scale_colour_hue(name="Hand",    # Legend label, use darker colors
                   breaks=c("Left", "Right"),
                   labels=c("Left", "Right"),
                   l=40) +                    # Use darker colors, lightness=40
  expand_limits(y=0) +                        # Expand y range
  scale_y_continuous(breaks=0:10*0.2) +     
  theme_bw() +
  theme(strip.background = element_rect(color = 'black',fill = 'NA',size = 1.2)) +
  theme(panel.background = element_rect(color = 'black',fill = 'NA',size = 1.2)) +
  stat_pvalue_manual(freq_pp, label ="p.adj.signif",
                     y.position = c(0.85,0.9),
                     xmin = "group1",xmax  = "group2",tip.length = 0,
                     step.group.by = "Hand",linetype ="Hand",
                     color = "Hand",position = pd)+
  labs(color  = "Hand", linetype = "Hand", group = "Hand") +
  theme(legend.box.just = "left",legend.justification = c(0.98,0.1), legend.position=c(0.98,0.1))+
  ggsave('graphs/op_trim_Rhythm.png',type='cairo', width= 6, height= 6, dpi = 800)
```

```{r}
ggarrange(a_speed, b_amp,c_fft, labels = c("a", "b", 'c'),
                    ncol = 1, nrow = 3)+
ggsave('graphs/op_measures.png',type='cairo', width= 5, height= 10, dpi = 800)
```


### Coeficient of variation between Peaks 

```{r echo=FALSE,include=FALSE}
detach("package:plyr", unload = TRUE)
```

```{r message=FALSE, warning=FALSE}
df_peaks <- df_ft_trim %>% dplyr::filter(!grepl("P64",ppid)) %>%
  select(ppid, Hand, trial_num, Device, pp, dist_norm,time) %>% 
  group_by(ppid,Hand,trial_num,Device) %>% 
  mutate(mean_dis = dist_norm - mean(dist_norm),
         is_peak = set_peaks_column(mean_dis)) %>% 
  dplyr::filter(is_peak) %>% 
  mutate(time_period = c(NA, diff(time))) %>% 
  dplyr::filter(!is.na(time_period)) %>% 
  mutate(Cov = sd(time_period)/mean(time_period),
         t = (row_number()*delta_t)-delta_t)
```



```{r include=FALSE}
df_covPeaks_op <- df_peaks %>% ungroup() %>% filter(Device == 'OPTOTRAK ')
```

#### Two-way ANOVA
```{r echo=FALSE}
cov_two.way <- aov(Cov ~ pp*Hand, data = df_covPeaks_op)
summary(cov_two.way)
```

#### SD, SE & CI
```{r echo=FALSE, message=FALSE, warning=FALSE}
CVpeaks_se_pp <- summarySE(df_covPeaks_op, measurevar="Cov", groupvars=c("Hand","pp"))
CVpeaks_se_pp
```

#### Tukey-HSD Test
```{r echo=FALSE}
CVpeaks_pp <- df_covPeaks_op %>%
  group_by(Hand) %>%
  tukey_hsd(Cov ~ pp)
CVpeaks_pp
```

```{r message=FALSE, warning=FALSE,echo=FALSE}
ggplot(CVpeaks_se_pp , aes(x=as.factor(pp), y=Cov, colour=Hand, group=Hand,linetype=Hand)) + 
  geom_errorbar(aes(ymin=(Cov-sd), ymax=(Cov+sd),
                    colour=Hand), size=1, width=.3, position=pd) +
  geom_line(position=pd) +
  geom_point(position=pd, size=3, shape=21, fill="white") + # 21 is filled circle
  xlab("") +
  ylab("CoV between Peaks") +
  scale_colour_hue(name="Hand",    # Legend label, use darker colors
                   breaks=c("Left", "Right"),
                   labels=c("Left", "Right"),
                   l=40) +                    # Use darker colors, lightness=40
  expand_limits(y=0) +                        # Expand y range
  scale_y_continuous(breaks=0:10*0.1) +     
  theme_bw() +
  theme(strip.background = element_rect(color = 'black',fill = 'NA',size = 1.2)) +
  theme(panel.background = element_rect(color = 'black',fill = 'NA',size = 1.2)) +
  stat_pvalue_manual(CVpeaks_pp, label ="p.adj.signif",
                     y.position = c(0.35,0.4),
                     xmin = "group1",xmax  = "group2",tip.length = 0,
                     step.group.by = "Hand",linetype ="Hand",
                     color = "Hand",position = pd)+
  labs(color  = "Hand", linetype = "Hand", group = "Hand") +
  theme(legend.box.just = "left",legend.justification = c(0.98,0.01), legend.position=c(0.98,0.01),
        legend.spacing.y = unit(0.1, 'cm'), legend.key.height = unit(0.5,'cm'))+
  ggsave('graphs/op_trim_CV_peaks.png',type='cairo', width= 4, height= 4, dpi = 800)
```



### Correlation & Regression (Original data)
Correlation between objective measures
#### Amplitude Variation
```{r message=FALSE, warning=FALSE, include=FALSE,echo=FALSE}
detach("package:plyr", unload = TRUE)
orig_big_amp_cor <- df_amplitude %>%  select(-dist_norm) %>% 
  dplyr::filter(Device == 'BIGKAT ') 

orig_op_amp_cor <- df_amplitude %>% ungroup() %>% select(-dist_norm) %>% 
  dplyr::filter(Device == 'OPTOTRAK ')

orig_df_amp_cor <- left_join(orig_op_amp_cor,orig_big_amp_cor,
                              by= c('t','trial_num','ppid','Hand','pp'), all= TRUE,)

orig_df_amp_cor<-orig_df_amp_cor[complete.cases(orig_df_amp_cor),]


orig_df_amp_cor_trials <- orig_df_amp_cor %>% select(-Device.x,-Device.y,-t) %>% 
  group_by(trial_num,ppid, Hand, pp) %>% 
  summarise(windows_CV.x = mean(windows_CV.x),
            windows_CV.y = mean(windows_CV.y)) %>% 
  arrange(ppid,Hand,trial_num)
# cor.test 

library(plyr)

# cor summary
orig_amplitude_cor_pp_allTrials_sum <- ddply(orig_df_amp_cor, .(pp),
                               summarise,z=corfun(windows_CV.x, windows_CV.y)$statistic,
                               pval=corfun(windows_CV.x, windows_CV.y)$p.value,
                               cor.est=corfun(windows_CV.x, windows_CV.y)$estimate,
                               alt=corfun(windows_CV.x, windows_CV.y)$alternative
)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}
a_amp_cor <- ggplot(orig_df_amp_cor_trials,aes(y = windows_CV.x, x = windows_CV.y,  color = as.factor(pp)))+
  geom_point(size=2,color = 'black',show.legend = FALSE) +
  stat_smooth(method = "lm",fullrange = T,show.legend = FALSE)+
  stat_smooth_func_with_pval(geom="text",
                             method="lm",
                             color = 'black',
                             hjust=0,
                             parse=TRUE,
                             xpos = 0,
                             ypos = 1,
                             size=3.5,
                             xpos2 = 0,
                             ypos2 = 0.8) +
  #coord_equal() +
  expand_limits(x = 0, y = 0) +
  scale_y_continuous(breaks=0:10*0.2) +
  labs(x = "BIGKAT", y = "Optotrak",color='width' )+
  theme_bw()+
  facet_grid(Hand~pp)+
  #coord_cartesian(xlim = c(0, 120),ylim = c(0,180))+
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black'))+
  theme(axis.ticks = element_blank())+
  scale_color_manual(values = c("tomato", "green"))+
  theme(legend.text=element_blank())+
  #theme(legend.title=element_text()) +
  theme(legend.title = element_blank())+
  ggsave("graphs/orig_comparison_amp.png", type = "cairo", width = 6, height = 5,dpi = 800)
```

#### Average Speed

```{r message=FALSE, warning=FALSE, include=FALSE,echo=FALSE}
detach("package:plyr", unload = TRUE)
orig_big_sp_cor <- df_speed_ave %>%  select(-dist_norm,-mean_dis,-is_peak,-speed_peak,-ave_speed_peak) %>%
  dplyr::filter(Device == 'BIGKAT ') 

orig_op_sp_cor <- df_speed_ave %>% ungroup() %>% select(-dist_norm,-mean_dis,-is_peak,-speed_peak,-ave_speed_peak) %>% 
  dplyr::filter(Device == 'OPTOTRAK ')

orig_df_sp_cor <- left_join(orig_op_sp_cor,orig_big_sp_cor,
                              by= c('t','trial_num','ppid','Hand','pp'), all= TRUE,)

orig_df_sp_cor<-orig_df_sp_cor[complete.cases(orig_df_sp_cor),]

orig_df_sp_cor_trials <- orig_df_sp_cor %>% select(-Device.x,-Device.y,-t) %>% 
  group_by(trial_num,ppid, Hand, pp) %>% 
  summarise(ave_speed.x = mean(ave_speed.x),
            ave_speed.y = mean(ave_speed.y)) %>% 
  arrange(ppid,Hand,trial_num)
# cor.test 

library(plyr)

# cor summary
orig_speed_cor_pp_allTrials_sum <- ddply(orig_df_sp_cor, .(Hand,pp),
                               summarise,z=corfun(ave_speed.x, ave_speed.y)$statistic,
                               pval=corfun(ave_speed.x, ave_speed.y)$p.value,
                               cor.est=corfun(ave_speed.x, ave_speed.y)$estimate,
                               alt=corfun(ave_speed.x, ave_speed.y)$alternative
)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
a_speed_cor <- ggplot(orig_df_sp_cor_trials,aes(y = ave_speed.x, x = ave_speed.y,  color = as.factor(pp)))+
  geom_point(size=2,color = 'black',show.legend = FALSE) +
  stat_smooth(method = "lm",fullrange = T,show.legend = FALSE)+
  stat_smooth_func_with_pval(geom="text",
                             method="lm",
                             color = 'black',
                             hjust=0,
                             parse=TRUE,
                             xpos = 0,
                             ypos = 7,
                             size=3.5,
                             xpos2 = 0,
                             ypos2 = 6) +
  #coord_equal() +
  expand_limits(x = 0, y = 0) +
  scale_y_continuous(breaks=0:8*2) +
  labs(x = "BIGKAT", y = "Optotrak",color='width' )+
  theme_bw()+
  facet_grid(Hand~pp)+
  #coord_cartesian(xlim = c(0, 120),ylim = c(0,180))+
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black'))+
  theme(axis.ticks = element_blank())+
  scale_color_manual(values = c("tomato", "green"))+
  theme(legend.text=element_blank())+
  #theme(legend.title=element_text()) +
  theme(legend.title = element_blank())
a_speed_cor + ggsave("graphs/orig_comparison_speed.png", type = "cairo", width = 6, height = 5,dpi = 800)
```

#### FFT Correlation

```{r message=FALSE, warning=FALSE, include=FALSE,echo=FALSE}
detach("package:plyr", unload = TRUE)
orig_big_fft_cor <- df_fft %>%  select(-dist_norm,-mean_dis,-time,-NFFT,-f) %>% 
  dplyr::filter(Device == 'BIGKAT ') 

orig_op_fft_cor <- df_fft %>% ungroup() %>% select(-dist_norm,-mean_dis,-time,-NFFT,-f) %>% 
  dplyr::filter(Device == 'OPTOTRAK ')

orig_df_fft_cor <- left_join(orig_op_fft_cor,orig_big_fft_cor,
                              by= c('t','trial_num','ppid','Hand','pp'), all= TRUE,)

orig_df_fft_cor<-orig_df_fft_cor[complete.cases(orig_df_fft_cor),]

orig_df_fft_cor_trials <- orig_df_fft_cor %>% select(-Device.x,-Device.y,-t) %>% 
  group_by(trial_num,ppid, Hand, pp) %>% 
  summarise(yf.x = mean(yf.x),
            yf.y = mean(yf.y),
            Freq_feature.x = mean(Freq_feature.x),
            Freq_feature.y = mean(Freq_feature.y)) %>% 
  arrange(ppid,Hand,trial_num)
# cor.test 

library(plyr)

orig_fft_cor_pp_sum <- ddply(orig_df_fft_cor_trials, .(pp),
                               summarise,z=corfun(Freq_feature.x, Freq_feature.y)$statistic,
                               pval=corfun(Freq_feature.x, Freq_feature.y)$p.value,
                               cor.est=corfun(Freq_feature.x, Freq_feature.y)$estimate,
                               alt=corfun(Freq_feature.x, Freq_feature.y)$alternative
)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
a_fft_cor <- ggplot(orig_df_fft_cor_trials,aes(y = Freq_feature.x, x = Freq_feature.y,  color = as.factor(pp)))+
  geom_point(size=2,color = 'black',show.legend = FALSE) +
  stat_smooth(method = "lm",fullrange = T,show.legend = FALSE)+
  stat_smooth_func_with_pval(geom="text",
                             method="lm",
                             color = 'black',
                             hjust=0,
                             parse=TRUE,
                             xpos = 0,
                             ypos = 1.2,
                             size=3.5,
                             xpos2 = 0,
                             ypos2 = 1) +
  #coord_equal() +
  expand_limits(x = 0, y = 0) +
   scale_y_continuous(breaks=0:10*0.2) +
  labs(x = "BIGKAT", y = "Optotrak",color='width' )+
  theme_bw()+
  facet_grid(Hand~pp)+
  #coord_cartesian(xlim = c(0, 120),ylim = c(0,180))+
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black'))+
  theme(axis.ticks = element_blank())+
  scale_color_manual(values = c("tomato", "green"))+
  theme(legend.text=element_blank())+
  #theme(legend.title=element_text()) +
  theme(legend.title = element_blank())
a_fft_cor +  ggsave("graphs/orig_comparison_fft.png", type = "cairo", width = 6, height = 5,dpi = 800)
```

#### Time Period Correlation

```{r message=FALSE, warning=FALSE, include=FALSE,echo=FALSE}
detach("package:plyr", unload = TRUE)
orig_big_cov_cor <- df_peaks %>%  select(-dist_norm,-mean_dis,-time,-is_peak) %>% 
  dplyr::filter(Device == 'BIGKAT ') 

orig_op_cov_cor <- df_peaks  %>% select(-dist_norm,-mean_dis,-time,-is_peak) %>% 
  dplyr::filter(Device == 'OPTOTRAK ')

orig_df_cov_cor <- left_join(orig_op_cov_cor,orig_big_cov_cor,
                              by= c('t','trial_num','ppid','Hand','pp'), all= TRUE,)

orig_df_cov_cor<-orig_df_cov_cor[complete.cases(orig_df_cov_cor),]

orig_df_cov_cor_trials <- orig_df_cov_cor %>% select(-Device.x,-Device.y,-t) %>% 
  group_by(trial_num,ppid, Hand, pp) %>% 
  summarise(time_period.x = mean(time_period.x),
            time_period.y = mean(time_period.y),
            Cov.x = mean(Cov.x),
            Cov.y = mean(Cov.y)) %>% 
  arrange(ppid,Hand,trial_num)
# cor.test 

library(plyr)

orig_cov_cor_pp_sum <- ddply(orig_df_cov_cor_trials, .(pp),
                               summarise,z=corfun(Cov.x, Cov.y)$statistic,
                               pval=corfun(Cov.x, Cov.y)$p.value,
                               cor.est=corfun(Cov.x, Cov.y)$estimate,
                               alt=corfun(Cov.x, Cov.y)$alternative
)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
a_peak_cor <- ggplot(orig_df_cov_cor_trials,aes(y = time_period.x, x = time_period.y,  color = as.factor(pp)))+
  geom_point(size=2,color = 'black',show.legend = FALSE) +
  stat_smooth(method = "lm",fullrange = T,show.legend = FALSE)+
  stat_smooth_func_with_pval(geom="text",
                             method="lm",
                             color = 'black',
                             hjust=0,
                             parse=TRUE,
                             xpos = 0,
                             ypos = 0.8,
                             size=3.5,
                             xpos2 = 0,
                             ypos2 = 0.65) +
  #coord_equal() +
  expand_limits(x = 0, y = 0) +
  scale_y_continuous(breaks=0:10*0.2) +
  labs(x = "BIGKAT", y = "Optotrak",color='width')+
  theme_bw()+
  facet_grid(Hand~pp)+
  #coord_cartesian(xlim = c(0, 120),ylim = c(0,180))+
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black'))+
  theme(axis.ticks = element_blank())+
  scale_color_manual(values = c("tomato", "green"))+
  theme(legend.text=element_blank())+
  #theme(legend.title=element_text()) +
  theme(legend.title = element_blank())
a_peak_cor + ggsave("graphs/orig_comparison_time_period_Peaks.png", type = "cairo", width = 6, height = 5,dpi = 800)
```



#### Absolute Distance


```{r message=FALSE, warning=FALSE, include=FALSE,echo=FALSE}
detach("package:plyr", unload = TRUE)
big_dis_cor <- df_ft_trim %>%  select(-dist_norm,-is_reaching,-speed,-time) %>% 
  dplyr::filter(Device == 'BIGKAT ')

op_dis_cor <- df_ft_trim %>% ungroup() %>% select(-dist_norm,-is_reaching,-speed,-time) %>% 
  dplyr::filter(Device == 'OPTOTRAK ')

df_dis_cor <- left_join(op_dis_cor,big_dis_cor,
                              by= c('t','trial_num','ppid','Hand','pp'), all= TRUE,)

df_dis_cor<-df_dis_cor[complete.cases(df_dis_cor),]
# cor.test 

df_dis_filt <- df_dis_cor %>% filter(ppid == " P72 ", Hand == " Left ", trial_num == " 1")

df_dis_full <- anti_join(df_dis_cor,df_dis_filt)


df_dis_cor_trials <- df_dis_full %>% select(-Device.x,-Device.y,-t) %>% 
  group_by(trial_num,ppid, Hand, pp) %>% 
  summarise(abs_dis.x = mean(abs_dis.x),
            abs_dis.y = mean(abs_dis.y)) %>% 
  arrange(ppid,Hand,trial_num)

library(plyr)

# cor summary
dis_cor_allTrials_sum <- ddply(df_dis_full, .(trial_num,ppid,Hand,pp),
                               summarise,z=corfun(abs_dis.x, abs_dis.y)$statistic,
                               pval=corfun(abs_dis.x, abs_dis.y)$p.value,
                               cor.est=corfun(abs_dis.x, abs_dis.y)$estimate,
                               alt=corfun(abs_dis.x, abs_dis.y)$alternative
) 
dis_cor_allTrials_sum <- dis_cor_allTrials_sum %>% arrange(ppid,Hand,trial_num) 

dis_cor_allTrials_sum %>% write.csv("abs_dis_cor_result_allTrials.csv")
dis_cor_allTrials_sum
```



```{r echo=FALSE}
ggplot(df_dis_cor_trials,aes(y = abs_dis.x, x = abs_dis.y,  color = as.factor(pp)))+
  geom_point(size=2,color = 'black',show.legend = FALSE) +
  stat_smooth(method = "lm",fullrange = T,show.legend = FALSE)+
  stat_smooth_func_with_pval(geom="text",
                             method="lm",
                             color = 'black',
                             hjust=0,
                             parse=TRUE,
                             xpos = 0,
                             ypos = 140,
                             size=3.5,
                             xpos2 = 0,
                             ypos2 = 110) +
  #coord_equal() +
  expand_limits(x = 0, y = 0) +
  labs(x = "BIGKAT", y = "Optotrak",color='width',tag = 'e' )+
  theme_bw()+
  facet_wrap(Hand~pp)+
  #coord_cartesian(xlim = c(0, 120),ylim = c(0,180))+
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black'))+
  theme(axis.ticks = element_blank())+
  scale_color_manual(values = c("tomato", "green"))+
  theme(legend.text=element_blank())+
  #theme(legend.title=element_text()) +
  theme(legend.title = element_blank())+
  ggsave("graphs/comparison_abs_dis.png", type = "cairo", width = 6, height = 5,dpi = 800)
```






### Correlation & Regression (Filtered Data)
Correlation between objective measures
#### Amplitude Variation
```{r message=FALSE, warning=FALSE, include=FALSE,echo=FALSE}
detach("package:plyr", unload = TRUE)
big_amp_cor <- df_amplitude %>%  select(-dist_norm) %>% 
  dplyr::filter(Device == 'BIGKAT ') 

op_amp_cor <- df_amplitude %>% ungroup() %>% select(-dist_norm) %>% 
  dplyr::filter(Device == 'OPTOTRAK ')

df_amp_cor <- left_join(op_amp_cor,big_amp_cor,
                              by= c('t','trial_num','ppid','Hand','pp'), all= TRUE,)

df_amp_cor<-df_amp_cor[complete.cases(df_amp_cor),]

df_amp_p72 <- df_amp_cor %>% filter(ppid == " P72 ", Hand == " Left ", trial_num == " 1")
df_amp_p83 <- df_amp_cor %>% filter(ppid == " P83 ", Hand == " Right ", trial_num == " 1")
df_amp_p75 <- df_amp_cor %>% filter(ppid == " P75 ", Hand == " Right ", trial_num == " 3")


df_amp_filt <- rbind(df_amp_p72,df_amp_p83,df_amp_p75)
df_amp_full <- anti_join(df_amp_cor,df_amp_filt)

df_amp_cor_trials <- df_amp_full %>% select(-Device.x,-Device.y,-t) %>% 
  group_by(trial_num,ppid, Hand, pp) %>% 
  summarise(windows_CV.x = mean(windows_CV.x),
            windows_CV.y = mean(windows_CV.y)) %>% 
  arrange(ppid,Hand,trial_num)
# cor.test 

library(plyr)

# cor summary
amplitude_cor_pp_allTrials_sum <- ddply(df_amp_cor, .(ppid,Hand,pp),
                               summarise,z=corfun(windows_CV.x, windows_CV.y)$statistic,
                               pval=corfun(windows_CV.x, windows_CV.y)$p.value,
                               cor.est=corfun(windows_CV.x, windows_CV.y)$estimate,
                               alt=corfun(windows_CV.x, windows_CV.y)$alternative
)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}
b_amp_cor <- ggplot(df_amp_cor_trials,aes(y = windows_CV.x, x = windows_CV.y,  color = as.factor(pp)))+
  geom_point(size=2,color = 'black',show.legend = FALSE) +
  stat_smooth(method = "lm",fullrange = T,show.legend = FALSE)+
  stat_smooth_func_with_pval(geom="text",
                             method="lm",
                             color = 'black',
                             hjust=0,
                             parse=TRUE,
                             xpos = 0,
                             ypos = 1,
                             size=3.5,
                             xpos2 = 0,
                             ypos2 = 0.8) +
  #coord_equal() +
  #expand_limits(x = 0, y = 0) +
  scale_y_continuous(breaks=0:10*0.2) +
  labs(x = "BIGKAT", y = "Optotrak",color='width')+
  theme_bw()+
  facet_grid(Hand~pp)+
  #coord_cartesian(xlim = c(0, 120),ylim = c(0,180))+
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black'))+
  theme(axis.ticks = element_blank())+
  scale_color_manual(values = c("tomato", "green"))+
  theme(legend.text=element_blank())+
  #theme(legend.title=element_text()) +
  theme(legend.title = element_blank())+
  ggsave("graphs/comparison_amp.png", type = "cairo", width = 6, height = 5,dpi = 800)
```

```{r}
ggarrange(a_amp_cor, b_amp_cor, labels = c("a", "b"),
                    ncol = 1, nrow = 2)+
ggsave('graphs/amp_regression.png',type='cairo', width= 7, height= 8, dpi = 800)
```


#### Average Speed

```{r message=FALSE, warning=FALSE, include=FALSE,echo=FALSE}
detach("package:plyr", unload = TRUE)
big_sp_cor <- df_speed_ave %>%  select(-dist_norm,-mean_dis,-is_peak,-speed_peak,-ave_speed_peak) %>% 
  dplyr::filter(Device == 'BIGKAT ') 

op_sp_cor <- df_speed_ave %>% ungroup() %>% select(-dist_norm,-mean_dis,-is_peak,-speed_peak,-ave_speed_peak) %>% 
  dplyr::filter(Device == 'OPTOTRAK ')

df_sp_cor <- left_join(op_sp_cor,big_sp_cor,
                              by= c('t','trial_num','ppid','Hand','pp'), all= TRUE,)

df_sp_cor<-df_sp_cor[complete.cases(df_sp_cor),]

df_sp_p71 <- df_sp_cor %>% filter(ppid == " P71 ", Hand == " Right ", trial_num == " 3")
df_sp_p72 <- df_sp_cor %>% filter(ppid == " P72 ", Hand == " Left ", trial_num == " 1")
df_sp_c05 <- df_sp_cor %>% filter(ppid == " C05 ", Hand == " Right ", trial_num == " 4")


df_sp_filt <- rbind(df_sp_p71,df_sp_p72,df_sp_c05)
df_sp_full <- anti_join(df_sp_cor,df_sp_filt)

df_sp_cor_trials <- df_sp_full %>% select(-Device.x,-Device.y,-t) %>% 
  group_by(trial_num,ppid, Hand, pp) %>% 
  summarise(ave_speed.x = mean(ave_speed.x),
            ave_speed.y = mean(ave_speed.y)) %>% 
  arrange(ppid,Hand,trial_num)
# cor.test 

library(plyr)

# cor summary
speed_cor_pp_allTrials_sum <- ddply(df_sp_cor, .(Hand,pp),
                               summarise,z=corfun(ave_speed.x, ave_speed.y)$statistic,
                               pval=corfun(ave_speed.x, ave_speed.y)$p.value,
                               cor.est=corfun(ave_speed.x, ave_speed.y)$estimate,
                               alt=corfun(ave_speed.x, ave_speed.y)$alternative
)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
b_speed_cor <- ggplot(df_sp_cor_trials,aes(y = ave_speed.x, x = ave_speed.y,  color = as.factor(pp)))+
  geom_point(size=2,color = 'black',show.legend = FALSE) +
  stat_smooth(method = "lm",fullrange = T,show.legend = FALSE)+
  stat_smooth_func_with_pval(geom="text",
                             method="lm",
                             color = 'black',
                             hjust=0,
                             parse=TRUE,
                             xpos = 0,
                             ypos = 7,
                             size=3.5,
                             xpos2 = 0,
                             ypos2 = 6) +
  #coord_equal() +
  expand_limits(x = 0, y = 0) +
  scale_y_continuous(breaks=0:8*2) +
  labs(x = "BIGKAT", y = "Optotrak",color='width',tag = 'b' )+
  theme_bw()+
  facet_grid(Hand~pp)+
  #coord_cartesian(xlim = c(0, 120),ylim = c(0,180))+
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black'))+
  theme(axis.ticks = element_blank())+
  scale_color_manual(values = c("tomato", "green"))+
  theme(legend.text=element_blank())+
  #theme(legend.title=element_text()) +
  theme(legend.title = element_blank())
b_speed_cor + ggsave("graphs/comparison_speed.png", type = "cairo", width = 6, height = 5,dpi = 800)
```

```{r}
ggarrange(a_speed_cor, b_speed_cor, labels = c("a", "b"),
                    ncol = 1, nrow = 2)+
ggsave('graphs/speed_regression.png',type='cairo', width= 7, height= 8, dpi = 800)
```


#### FFT Correlation

```{r message=FALSE, warning=FALSE, include=FALSE,echo=FALSE}
detach("package:plyr", unload = TRUE)
big_fft_cor <- df_fft %>%  select(-dist_norm,-mean_dis,-time,-NFFT,-f) %>% 
  dplyr::filter(Device == 'BIGKAT ') 

op_fft_cor <- df_fft %>% ungroup() %>% select(-dist_norm,-mean_dis,-time,-NFFT,-f) %>% 
  dplyr::filter(Device == 'OPTOTRAK ')

df_fft_cor <- left_join(op_fft_cor,big_fft_cor,
                              by= c('t','trial_num','ppid','Hand','pp'), all= TRUE,)

df_fft_cor<-df_fft_cor[complete.cases(df_fft_cor),]

df_fft_c06 <- df_fft_cor %>% filter(ppid == " C06 ", Hand == " Left ", trial_num == " 4")
df_fft_p72 <- df_fft_cor %>% filter(ppid == " P72 ", Hand == " Left ", trial_num == " 1")

df_fft_c05 <- df_fft_cor %>% filter(ppid == " C05 ", Hand == " Right ", trial_num == " 4")

df_fft_p78 <- df_fft_cor %>% filter(ppid == " P78 ", Hand == " Right ", trial_num == " 4")



df_fft_filt <- rbind(df_fft_c06,df_fft_p72,df_fft_c05,df_fft_p78)
df_fft_full <- anti_join(df_fft_cor,df_fft_filt)



df_fft_cor_trials <- df_fft_full %>% select(-Device.x,-Device.y,-t) %>% 
  group_by(trial_num,ppid, Hand, pp) %>% 
  summarise(yf.x = mean(yf.x),
            yf.y = mean(yf.y),
            Freq_feature.x = mean(Freq_feature.x),
            Freq_feature.y = mean(Freq_feature.y)) %>% 
  arrange(ppid,Hand,trial_num)
# cor.test 

library(plyr)

fft_cor_pp_sum <- ddply(df_fft_cor_trials, .(ppid,Hand,pp),
                               summarise,z=corfun(Freq_feature.x, Freq_feature.y)$statistic,
                               pval=corfun(Freq_feature.x, Freq_feature.y)$p.value,
                               cor.est=corfun(Freq_feature.x, Freq_feature.y)$estimate,
                               alt=corfun(Freq_feature.x, Freq_feature.y)$alternative
)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
b_fft_cor <- ggplot(df_fft_cor_trials,aes(y = Freq_feature.x, x = Freq_feature.y,  color = as.factor(pp)))+
  geom_point(size=2,color = 'black',show.legend = FALSE) +
  stat_smooth(method = "lm",fullrange = T,show.legend = FALSE)+
  stat_smooth_func_with_pval(geom="text",
                             method="lm",
                             color = 'black',
                             hjust=0,
                             parse=TRUE,
                             xpos = 0,
                             ypos = 1.2,
                             size=3.5,
                             xpos2 = 0,
                             ypos2 = 1) +
  #coord_equal() +
  expand_limits(x = 0, y = 0) +
  scale_y_continuous(breaks=0:10*0.2) +
  labs(x = "BIGKAT", y = "Optotrak",color='width' )+
  theme_bw()+
  facet_grid(Hand~pp)+
  #coord_cartesian(xlim = c(0, 120),ylim = c(0,180))+
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black'))+
  theme(axis.ticks = element_blank())+
  scale_color_manual(values = c("tomato", "green"))+
  theme(legend.text=element_blank())+
  #theme(legend.title=element_text()) +
  theme(legend.title = element_blank())
b_fft_cor + ggsave("graphs/comparison_fft.png", type = "cairo", width = 6, height = 5,dpi = 800)
```

```{r}
ggarrange(a_fft_cor, b_fft_cor, labels = c("a", "b"),
                    ncol = 1, nrow = 2)+
ggsave('graphs/fft_regression.png',type='cairo', width= 7, height= 8, dpi = 800)
```

#### Time Period Correlation

```{r message=FALSE, warning=FALSE, include=FALSE,echo=FALSE}
detach("package:plyr", unload = TRUE)
big_cov_cor <- df_peaks %>%  select(-dist_norm,-mean_dis,-time,-is_peak) %>% 
  dplyr::filter(Device == 'BIGKAT ') 

op_cov_cor <- df_peaks  %>% select(-dist_norm,-mean_dis,-time,-is_peak) %>% 
  dplyr::filter(Device == 'OPTOTRAK ')

df_cov_cor <- left_join(op_cov_cor,big_cov_cor,
                              by= c('t','trial_num','ppid','Hand','pp'), all= TRUE,)

df_cov_cor<-df_cov_cor[complete.cases(df_cov_cor),]

# df_fft_c06 <- df_cov_cor %>% filter(ppid == " C06 ", Hand == " Left ", trial_num == " 4")
# df_fft_p72 <- df_cov_cor %>% filter(ppid == " P72 ", Hand == " Left ", trial_num == " 1")
# 
# df_fft_c05 <- df_cov_cor %>% filter(ppid == " C05 ", Hand == " Right ", trial_num == " 4")
# 
# df_fft_p78 <- df_cov_cor %>% filter(ppid == " P78 ", Hand == " Right ", trial_num == " 4")
# 
# 
# 
# df_fft_filt <- rbind(df_cov_c06,df_fft_p72,df_fft_c05,df_fft_p78)
# df_fft_full <- anti_join(df_fft_cor,df_fft_filt)



df_cov_cor_trials <- df_cov_cor %>% select(-Device.x,-Device.y,-t) %>% 
  group_by(trial_num,ppid, Hand, pp) %>% 
  summarise(time_period.x = mean(time_period.x),
            time_period.y = mean(time_period.y),
            Cov.x = mean(Cov.x),
            Cov.y = mean(Cov.y)) %>% 
  arrange(ppid,Hand,trial_num)
# cor.test 

library(plyr)

cov_cor_pp_sum <- ddply(df_cov_cor_trials, .(ppid,Hand,pp),
                               summarise,z=corfun(Cov.x, Cov.y)$statistic,
                               pval=corfun(Cov.x, Cov.y)$p.value,
                               cor.est=corfun(Cov.x, Cov.y)$estimate,
                               alt=corfun(Cov.x, Cov.y)$alternative
)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
b_peak_cor <- ggplot(df_cov_cor_trials,aes(y = time_period.x, x = time_period.y,  color = as.factor(pp)))+
  geom_point(size=2,color = 'black',show.legend = FALSE) +
  stat_smooth(method = "lm",fullrange = T,show.legend = FALSE)+
  stat_smooth_func_with_pval(geom="text",
                             method="lm",
                             color = 'black',
                             hjust=0,
                             parse=TRUE,
                             xpos = 0,
                             ypos = 0.8,
                             size=3.5,
                             xpos2 = 0,
                             ypos2 = 0.65) +
  #coord_equal() +
  expand_limits(x = 0, y = 0) +
    scale_y_continuous(breaks=0:10*0.2) +
  labs(x = "BIGKAT", y = "Optotrak",color='width' )+
  theme_bw()+
  facet_wrap(Hand~pp)+
  #coord_cartesian(xlim = c(0, 120),ylim = c(0,180))+
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black'))+
  theme(axis.ticks = element_blank())+
  scale_color_manual(values = c("tomato", "green"))+
  theme(legend.text=element_blank())+
  #theme(legend.title=element_text()) +
  theme(legend.title = element_blank())
b_peak_cor + ggsave("graphs/comparison_time_period_Peaks.png", type = "cairo", width = 6, height = 5,dpi = 800)
```
```{r}
ggarrange(a_peak_cor, b_peak_cor, labels = c("a", "b"),
                    ncol = 1, nrow = 2)+
ggsave('graphs/peak_regression.png',type='cairo', width= 7, height= 8, dpi = 800)
```


#### Absolute Distance


```{r message=FALSE, warning=FALSE, include=FALSE,echo=FALSE}
detach("package:plyr", unload = TRUE)
big_dis_cor <- df_ft_trim %>%  select(-dist_norm,-is_reaching,-speed,-time) %>% 
  dplyr::filter(Device == 'BIGKAT ')

op_dis_cor <- df_ft_trim %>% ungroup() %>% select(-dist_norm,-is_reaching,-speed,-time) %>% 
  dplyr::filter(Device == 'OPTOTRAK ')

df_dis_cor <- left_join(op_dis_cor,big_dis_cor,
                              by= c('t','trial_num','ppid','Hand','pp'), all= TRUE,)

df_dis_cor<-df_dis_cor[complete.cases(df_dis_cor),]
# cor.test 

df_dis_filt <- df_dis_cor %>% filter(ppid == " P72 ", Hand == " Left ", trial_num == " 1")

df_dis_full <- anti_join(df_dis_cor,df_dis_filt)


df_dis_cor_trials <- df_dis_full %>% select(-Device.x,-Device.y,-t) %>% 
  group_by(trial_num,ppid, Hand, pp) %>% 
  summarise(abs_dis.x = mean(abs_dis.x),
            abs_dis.y = mean(abs_dis.y)) %>% 
  arrange(ppid,Hand,trial_num)

library(plyr)

# cor summary
dis_cor_allTrials_sum <- ddply(df_dis_full, .(trial_num,ppid,Hand,pp),
                               summarise,z=corfun(abs_dis.x, abs_dis.y)$statistic,
                               pval=corfun(abs_dis.x, abs_dis.y)$p.value,
                               cor.est=corfun(abs_dis.x, abs_dis.y)$estimate,
                               alt=corfun(abs_dis.x, abs_dis.y)$alternative
) 
dis_cor_allTrials_sum <- dis_cor_allTrials_sum %>% arrange(ppid,Hand,trial_num) 

dis_cor_allTrials_sum %>% write.csv("abs_dis_cor_result_allTrials.csv")
dis_cor_allTrials_sum
```



```{r echo=FALSE}
ggplot(df_dis_cor_trials,aes(y = abs_dis.x, x = abs_dis.y,  color = as.factor(pp)))+
  geom_point(size=2,color = 'black',show.legend = FALSE) +
  stat_smooth(method = "lm",fullrange = T,show.legend = FALSE)+
  stat_smooth_func_with_pval(geom="text",
                             method="lm",
                             color = 'black',
                             hjust=0,
                             parse=TRUE,
                             xpos = 0,
                             ypos = 140,
                             size=3.5,
                             xpos2 = 0,
                             ypos2 = 110) +
  #coord_equal() +
  expand_limits(x = 0, y = 0) +
  labs(x = "BIGKAT", y = "Optotrak",color='width',tag = 'e' )+
  theme_bw()+
  facet_wrap(Hand~pp)+
  #coord_cartesian(xlim = c(0, 120),ylim = c(0,180))+
  theme(strip.background =element_rect(fill="white"))+
  theme(strip.text = element_text(colour = 'black'))+
  theme(axis.ticks = element_blank())+
  scale_color_manual(values = c("tomato", "green"))+
  theme(legend.text=element_blank())+
  #theme(legend.title=element_text()) +
  theme(legend.title = element_blank())+
  ggsave("graphs/comparison_abs_dis.png", type = "cairo", width = 6, height = 5,dpi = 800)
```
